---
title: "525 Final"
author: "Xinqian Dai"
date: '2022-10-29'
output: pdf_document
---
R code for turning year to decade:
```{r}
disney<-disney%>% filter(year>=1984)
# not much data before year 1984
disney<-disney%>% mutate(round_to_decade = round(year / 10) * 10)
# This step round year to its nearest decade number.(eg. 1902->1900, 1908->1910)
disney$round_to_decade<-as.factor(disney2$round_to_decade)
# turn roundup year to factor instead of numeric data
```
R code for summary table:
```{r}
disney<-disney%>% mutate(budget_m=budget/1000000)
mean(disney$total_gross_m)
sd(disney$total_gross_m)
mean(disney$budget_m)
sd(disney$budget_m)
mean(disney$rating)
sd(disney$rating)
mean(disney$length)
sd(disney$length)
mean(disney$year)
sd(disney$year)
```
R code for added-variable plots:
```{r}
avPlots(fit)
```
R code for Scatterplots:
```{r}
disney %>% ggplot(aes(x=budget_m, y=total_gross_m)) + geom_point(color="blue") + ggtitle(label = "Budget In
Millions VS Total Gross In Millions") + labs(x = "Budget", y = "Total Gross")
disney %>% ggplot(aes(x=rating, y=total_gross_m)) + geom_point(color="red") + ggtitle(label = "Rating VS Total
Gross In Millions") + labs(x = "Rating", y = "Total Gross")
disney %>% ggplot(aes(x=length, y=total_gross_m)) + geom_point(color="green") + ggtitle(label = "Length VS
Total Gross In Millions") + labs(x = "Length", y = "Total Gross")
disney %>% ggplot(aes(x=year, y=total_gross_m)) + geom_point(color="pink") + ggtitle(label = "Years VS Total
Gross In Millions") + labs(x = "Year", y = "Total Gross")
```
R code for Boxplots:
```{r}
boxplot(total_gross_m ~genre, data = disney, xlab="Genre",ylab="Total Gross")
boxplot(total_gross_m ~mpaa_rating, data = disney, xlab="MPAA Rating",ylab="Total Gross")
boxplot(total_gross_m ~month, data = disney, xlab="Month",ylab="Total Gross")
```
R code for simple linear regressions:
```{r}
fit_budget <- lm(total_gross_m~budget_m,data=data)
fit_rating <- lm(total_gross_m~rating,data=data)
fit_length <- lm(total_gross_m~length,data=data)
fit_year <- lm(total_gross_m~year,data=data)
summary(fit_budget)
summary(fit_rating)
summary(fit_length)
summary(fit_year)
```
R code for multiple interactive and additive regression:
```{r}
disney1<-disney%>% select(total_gross_m,budget_m,rating,length,year)
fit<-lm(total_gross_m~.,data=disney1)
summary(fit)
fit_interact<-lm(total_gross_m~.^2,data = disney1)
summary(fit_interact)
anova(fit,fit_interact)
disney1<-disney2%>% select(total_gross_m,budget_m,rating,length,round_to_decade,mpaa_rating)
new.fit<-lm(total_gross_m~.,data = disney1)
summary(new.fit)
new.interaction.fit<-lm(total_gross_m~.^2,data=disney1)
anova(new.fit,new.interaction.fit)
summary(new.interaction.fit)
disney.n<-disney1[-6]
no.decade.interaction<-lm(total_gross_m~.^2,disney.n)
anova(new.interaction.fit,no.decade.interaction)